\section{High-Definition Multimedia Interface (HDMI)}
We chose HDMI to show the output result from the FPGA.
The HDMI cable can carry audio, Ethernet and other information in addition to the video stream itself, but only the video stream was utilized for this project.

\subsection{Transition-Minimized Differential Signaling}
Transition-Minimized Differential Signaling(TMDS) is a standard used for transmitting video data over HDMI. HDMI uses it at the physical layer, and our implementation use the native TMDS I/O interface that is featured by the Spartan-6 FPGAs.
Four channels of serial data establish the HDMI video transmission. It has three channels for the RBG color information and one for the pixel data rate clock. Each pixel has a 24-bit color depth, with each color being 8 bits each. These are separately convertered into 10-bit symbols before being serialized and transmitted onto the TMDS data channels. It is this 10:1 serialization ratio that makes the bit rate 10x faster than the actual pixel rate. During the video transmission the pixel symbol is periodically interlaced with four distinct control tokens representing blanking intervals. These control tokens provide accurate video line scan(HSYNC) and frame update(VSYNC) information. Control tokens are also used to identify word boundaries for synchronization purposes.


The technology is based on twisted pairs of cables transferring data using a differential encoding.
This encoding uses two cables for each bit and inverts the voltage difference between the cables in a pair whenever the bit represented by the pair should change.
Notice that, for the same voltage, this doubles the distance between the high and low states compared to using only a single cable and ground.
The lack of a need for a common ground also eliminates problems related to ground offset

TMDS transfers 10 bits at a time using an encoding that minimizes the number of transitions required between each set of bits.

\subsection{Implementation}
Our implementation of HDMI was based on the Xilinx application note 495(TODO: referanse) and its reference design files. In our implementation it is possible to take an HDMI input, do convolution on the input and then transmit the result as HDMI output. As our PCB consists of two HDMI connectors, it is possible to do this. Another way is getting the image data from the MCU or directly from the camera through the FPC connector, do convolution and then send the result as HDMI output.
