\section{Digital Video} \label{sec:DigitalVideo}
Video can be encoded in a variety of formats, each with its advantages and drawbacks.
In this project, a balance between quality, size and performance must be found,
such that the required throughput can be minimised without sacrificing too much image quality.

A common encoding for images is to encode the pixels in a two-dimensional array in a row-major order, in other words as an array of scanlines.

\subsection{Resolution}
The number of pixels in each scanline and the number of scanlines, more commonly referred to as the width and height of the image, determines the size of each pixel on the screen.

Too few pixels results in a "pixelated" image where the pixels are distinct.
Too many pixels gives a huge performance penalty as higher resolutions require more storage space and throughput.

\subsection{Colours}
Each element stored must provide the colour of the pixel it represents.

\subsubsection{Separate Components}
One way of achieving this goal is to separate the colour into three components and store each individually.
A common choice of components is red, green and blue, giving rise to the RGB colour model.

Furthermore, it is possible to store each component as a separate pixel or to interlace the different components in the same image so that all the information required to determine the colour of a pixel resides in one place.

As data stored by computers is discrete and of limited size, the number of values available when describing the amount of each component present in a given colour is limited.
The number of values that can be represented is referred to as the \textit{depth} of the image, commonly given in the number of bits used to represent a single value.

\subsubsection{Indexed}
Another way to store the colour information is to select a set of colours and assign each colour a number.
This is especially useful when reducing the size of an image by reducing the number of available colours.
With an index colour representation, the most commonly used colours can be selected and assigned numbers, thus reducing the error introduced by forcing the colours into a smaller space.

\subsection{Bit Rates}
An important measure in determining the efficiency of a given video format is the bit rate, the rate at which bits needs to be provided in order to display the video.
For uncompressed video, knowledge of the frame rate in addition to the image resolution and colour representation is necessary to be able to determine the bit rate of the video.

Table \ref{tab:BitRates} displays the bit rate required at some common resolutions, depths/index sizes and frame rates.
\begin{table}[h]
    \centering
    \begin{tabular}{ccrrr}
        Resolution & Depth/index size & Bit rate @ 15Hz & Bit rate @ 30Hz & Bit rate @ 60Hz \\
        \hline
        320x240 & 8 bit & 9,2 Mbps   & 18,4 Mbps  & 36,9 Mbps  \\
        320x240 & 16 bit & 18,4 Mbps  & 36,9 Mbps  & 73,7 Mbps  \\
        320x240 & 24 bit & 27,6 Mbps  & 55,3 Mbps  & 110,6 Mbps \\
        640x480 & 8 bit & 36,9 Mbps  & 73,7 Mbps  & 147,5 Mbps \\
        640x480 & 16 bit & 73,7 Mbps  & 147,5 Mbps & 294,9 Mbps \\
        640x480 & 24 bit & 110,6 Mbps & 221,2 Mbps & 442,4 Mbps
    \end{tabular}
    \caption{Bit rates given different video parameters.}
    \label{tab:BitRates}
\end{table}
