\section{Results}

In this section we present TODO.

\subsection{Scalability}
What convolution kernel matrix sizes can we handle, what image resolutions and depths... TODO: Add more text.
As stated in section \ref{sub:processor}, the processor has several parameters, some of which are hard coded into the final design.
These parameters can be adjusted, but many are limited by the available hardware.

According to the reports produced by Xilinx ISE during building of the FPGA bit file, our design for 3x3 convolution utilized around \unit[16]{\%} of the total number of available slices.
This includes many slices with unused components.

TODO:

The same report states the processor can be clocked at a maximum frequency of \emph{<insert frequency>}. This was however tested in practice as the processor was expected to deliver data quickly enough at lower frequencies.

\subsection{Performance}
Performance was the main focus of our project.

TODO: Add more info on achieved throughput given image format, convolution kernel matrix size...

\subsubsection{EBI Throughput} \label{subsec:EbiThroughput}
During the project, the throughput over EBI between a EFM MCU and a Spartan-6 FPGA was tested by sending a sequence of increasing number which were verified on the FPGA.
A set-up time of 1 cycle was required in addition to the mandatory cycle always introduced by the MCU EBI controller for data to be transferred correctly.

Since the MCU is running with a clock speed of 48MHz, this resulted in a maximum throughput of $\unit[16]{bits} \cdot \unit[48]{MHz} / 2 = \unit[384]{Mbps}$.
From Table \ref{tab:BitRates}, we can conclude this is sufficient to accommodate all options listed except the most data intensive.

During the testing, a default FIFO queue implementation from Xilinx was used to cross the clock domain.
As EBI is asynchronous and therefore does not provide a clock, the last value sent was not received on the FPGA.
As a workaround, a final \textit{don't care} value was sent over the bus to push the final data value through the FIFO at the FPGA.

\subsubsection{SRAM Throughput} \label{subsec:SramThroughput}
During SRAM testing, several clock rates were tried to determine the speed achievable to SRAM.
After some binary search through the frequency spectrum, $\unit[49]{MHz}$ proved to be working.
This gives a throughput of $\unit[49]{MHz}\cdot\unit[16]{bit} = \unit[784]{Mbps}$ for reading.
During writing however, this number must be halved as a write requires two cycles (one for address set-up and one for writing), giving a throughput for writing of $\unit[392]{Mbps}$.
